---
title: "wi_sem_team_14_plotting"
author: "Chris"
date: "7/11/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
# using pacman to laod and install any packages
install.packages("pacman")

# load packages
pacman::p_load(pacman, tidyverse, rio, dplyr, ggplot2, plotly, tidyr, rmarkdown, tinytex, lubridate)

knitr::opts_chunk$set(echo = TRUE)
```


```{r dataloading, include=FALSE}
# read dataset
data_event_log <- read_delim(
  "../data/event_log.csv",
  delim=';'
)
```

Short summary of the raw dataset
```{r summary, include=TRUE}
summary(data_event_log)
head(data_event_log)
```

Wertebereich für interessante Spalten ausgeben
```{r uniques}
unique(data_event_log$ACTIVITY)
unique(data_event_log$DEVICETYPE)
unique(data_event_log$SERVICEPOINT)
unique(data_event_log$REPAIR_IN_TIME_5D)
```

## Data cleaning

```{r data_cleaning, echo=FALSE}
# cleaning the data
# exclude rows containing null-values
clean_logs <- na.omit(data_event_log)
corrupted_logs <- subset(data_event_log,
                          is.na(DEVICETYPE) | 
                          is.na(SERVICEPOINT)
                         )
df_clean_logs <- as.data.frame(do.call(cbind, clean_logs))

df_clean_logs$TIMESTAMP <- as.POSIXct(clean_logs$TIMESTAMP, tz="",format="%Y-%m-%d %H:%M:%OS", optional = FALSE)
```

Some data exploration

```{r data_exploration, echo=FALSE}
print('Number of datapoint in the clean dataset:')
nrow(df_clean_logs)
print("Number of unique case IDs:")
unique(clean_logs$CASE_ID) %>% length()
```
### Some data modification

* creating column DATE (timestamps without the time information)
* creating column WEEKDAY (not sure if we need this as a column in the dataset, can just compute it insitro when needed)

```{r data_modification, echo=FALSE}
df_cl_mod <- df_clean_logs

# creating DATE column (calculating for each row)
df_cl_mod$DATE <- with(df_clean_logs, as.Date(TIMESTAMP))

# creating WEEKDAY column
df_cl_mod$WEEKDAY <- weekdays(df_cl_mod$DATE)

sleeper_cases <- c("Case5304", "Case5502", "Case5544")

df_sleeper_cases <- df_clean_logs[df_cl_mod$CASE_ID%in%sleeper_cases,]
df_cl_mod <- df_cl_mod[!(df_clean_logs$CASE_ID%in%sleeper_cases),]


```

```{r save_modifed_data}
# writing the modified df to csv with relative path to the folder "data"
write.csv(df_clean_logs, "../data/modified_logs.csv")
```


## Basic univariate plotting

our quantitative variables are :

* NONE ??

our qualitative variables are:

* CASE_ID (not sure tbh, bc this is part of the "primary key" of the dataset entities) {string} <- maybe convert to integer for easier processing
* ACTIVITY {string}
* SERVICEPOINT {char}
* DEVICETYPE {string}
* REPAIR_IN_TIME {double} <- maybe convert to boolean for easier processing

neither?:

* TIMESTAMP {double - feels more like a string tho}

### Plotting the frequency of our qualitative variables:
```{r univariate_plotting, echo=FALSE}
# activity count
activity_count <- table(clean_logs$ACTIVITY)
barplot(main="logs per activitytype", activity_count)

# rep in time
timely_repair <- table(clean_logs$REPAIR_IN_TIME_5D)
barplot(main="repair in time", timely_repair)

# logs per devicetype
devicetypes_counter <- table(clean_logs$DEVICETYPE)
barplot(main="logs per devicetype", devicetypes_counter)

# servicepoints
servicepoints <- table(clean_logs$SERVICEPOINT)
barplot(main="logs per servicepoint",servicepoints)
```















